---
title: "App Financiera"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    theme: yeti
    


---

<style>

.navbar-inverse {
    background-color: #000000;
    border-color: #5d5d5d;
}

.navbar-inverse .navbar-nav>li>a:focus {
    color: #f3f3f3;
    background-color: transparent;
}

.navbar-inverse .navbar-nav>.active>a, .navbar-inverse .navbar-nav>.active>a:hover, .navbar-inverse .navbar-nav>.active>a:focus {
    color: #ffffff;
    background-color: transparent;
}

.chart-stage-flex {
  overflow: scroll !important;
}


</style>





```{r setup, include=FALSE}

library(flexdashboard)
library(dplyr)
library(tidyverse)
library(lubridate)
library(rlang)
library(shiny)
library(DT)


fecha_hoy <- Sys.Date()
today <- as.Date(format(with_tz(fecha_hoy, tz = "America/Argentina/Buenos_Aires"), "%Y-%m-%d"))



valuebox = function(porcentaje, name, mensaje, color, font) {
  valueBox(
    value = tags$p(paste0(porcentaje, ' %'),
                   style = color), 
    icon = "fa-line-chart",
    caption = tags$p(paste0(mensaje, ' variacion Interanual: ',str_to_title(gsub("_", " ", name))), 
                     style = font),
    color =  color)
  
}



resultado <- read.csv("archivo.csv")


```







Panel General {data-orientation=rows}
=====================================

**Ultima actualización con datos del `r today`**



Row  {data-height=125}
-----------------------------------------------------------------------

### ***EMAE interanual***




```{r}



valuebox(1, name= "EMAE",mensaje = "EMAE", color="rgb(232, 221, 64)", font="font-size: 100%; color: #291e1e")

```




### ***Mayor suba interanual.***


```{r}


valuebox(1, name= "a", mensaje = "Mayor" , color="#800000", font="font-size: 100%; color: #ffffff")

```


### ***Menor suba interanual.***


```{r}

valuebox(1, name= "b", mensaje = "Menor",color="#a61425", font="font-size: 100%; color: #ffffff")

```


Row 
-----------------------------------------------------------------------

### ***Panel de Datos***


```{r}

brksVariacion <- quantile(resultado$Variacion, probs = seq(.05, .95, .05), na.rm = TRUE)
ramp <- colorRampPalette(c("#f52f2f", "#3bf557"))
clrsVariacion <- ramp(length(brksVariacion)+1)

datatable(
  resultado %>% 
    select(Especie, Variacion, InterAnual, DiasUltMax, TrendActual), 
  options = list(
        scrollY="100vh",
        scrollCollapse = FALSE
      )) %>% 
  formatStyle(
    'InterAnual',
    backgroundColor = styleInterval(c(0,50,100), c('#858f86','#91bd98', '#68de79','#3bf557'))
  )  %>%
  formatStyle(
    'DiasUltMax',
    background = styleColorBar(resultado$DiasUltMax, '#93badb'),
    backgroundSize = '100% 90%',
    backgroundRepeat = 'no-repeat',
    backgroundPosition = 'center'
  ) %>%
  formatStyle(
    'Variacion',
    backgroundColor = styleInterval(brksVariacion, clrsVariacion)
    ) %>%
  formatStyle(
    'TrendActual',
    backgroundColor = styleEqual(c("Alza","Baja"),c("#3bf557",  "#f52f2f"))
    )

```



